Response to the defense feedback

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

We consider an access-based attack~\cite{DBLP:journals/jce/GeYCH18}, where an adversary can probe one time for each run only after the termination of a deterministic program. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the chapter. It is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Similar to recent work, we assume the attacker has a noise-free observation.  The program ($\beta$) has $K$ as the sensitive input, which is a finite set consisted of every possible key ($k \in K$). The program also takes known messages $M$ as the input.

>>>>

We consider an access-based attack~\cite{ge2018survey}, where an adversary can probe one time for each run only after the termination of a deterministic program. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the chapter. It is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Similar to recent work, we assume the attacker has a noise-free observation.  The program ($\beta$) has $K$ as the sensitive input, which is a finite set consisted of every possible key ($k \in K$). The program also takes known messages $M$ as the input.
